PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
added code to create and merge all forest plot datasets

lm.forest <- function(data,title)

@@

>>>>

lm.forest <- function(data,title){

@@

## Create data frames and plots using functions and models generated above.

```{r generate datasets for all plots}
# prepandemic and retrospective, grouped by disorder measure
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")

lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","PHQ-9", "phq.prepan.lm.for.plot")
lmoutput_format(phq.retro.lm,"phq.sum_score_retro","PHQ-9", "phq.retro.lm.for.plot")

lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","PCL", "pcl.prepan.lm.for.plot")
lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","PCL", "pcl.retro.lm.for.plot")

# Retrospective, grouped by sample
lmoutput_format(gad.retro.lm.glad,"gad.sum_score_retro","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
lmoutput_format(gad.retro.lm.nbr,"gad.sum_score_retro","NBR", "gad.retro.lm.for.plot.NBR")
lmoutput_format(gad.retro.lm.ramp,"gad.sum_score_retro","RAMP", "gad.retro.lm.for.plot.RAMP")

lmoutput_format(phq.retro.lm.glad,"phq.sum_score_retro","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
lmoutput_format(phq.retro.lm.nbr,"phq.sum_score_retro","NBR", "phq.retro.lm.for.plot.NBR")
lmoutput_format(phq.retro.lm.ramp,"phq.sum_score_retro","RAMP", "phq.retro.lm.for.plot.RAMP")

lmoutput_format(pcl.retro.lm.glad,"pcl.sum_score_retro","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
lmoutput_format(pcl.retro.lm.nbr,"pcl.sum_score_retro","NBR", "pcl.retro.lm.for.plot.NBR")
lmoutput_format(pcl.retro.lm.ramp,"pcl.sum_score_retro","RAMP", "pcl.retro.lm.for.plot.RAMP")

```{r merge datasets for different combinations}
# Disorder groups
plot.dat.disorder.prepan <- rbind(gad.prepan.lm.for.plot,
                                  phq.prepan.lm.for.plot,
                                  pcl.prepan.lm.for.plot)

plot.dat.disorder.retro <- rbind(gad.retro.lm.for.plot,
                                  phq.retro.lm.for.plot,
                                  pcl.retro.lm.for.plot)

# time of rating groups
plot.dat.time.gad <- rbind(gad.prepan.lm.for.plot.timegroup,
                           gad.retro.lm.for.plot.timegroup)

plot.dat.time.phq <- rbind(phq.prepan.lm.for.plot.timegroup,
                           phq.retro.lm.for.plot.timegroup)

plot.dat.time.pcl <- rbind(pcl.prepan.lm.for.plot.timegroup,
                           pcl.retro.lm.for.plot.timegroup)

# by sample (for retrospective)

plot.dat.sample.gad <- rbind(gad.retro.lm.for.plot.GLAD,
                             gad.retro.lm.for.plot.NBR,
                             gad.retro.lm.for.plot.RAMP)

plot.dat.sample.phq <- rbind(phq.retro.lm.for.plot.GLAD,
                             phq.retro.lm.for.plot.NBR,
                             phq.retro.lm.for.plot.RAMP)

plot.dat.sample.pcl <- rbind(pcl.retro.lm.for.plot.GLAD,
                             pcl.retro.lm.for.plot.NBR,
                             pcl.retro.lm.for.plot.RAMP)
